 

### 2021-09-01 vertical-thermal-review_SI.Rmd
first pass at table, knit into document
Co-Authored-By: Marielle N Smith <45404993+m-n-smith@users.noreply.github.com>

#  Appendix `r appendix_NEON_methods`. `r appendix_NEON_methods_title`

@@

#  Appendix `r appendix_tealeaves_methods`. `r appendix_tealeaves_methods_title`

@@

@@

Make a table from this:
https://github.com/EcoClimLab/vertical-thermal-review/blob/master/NEON_height_profiles/HARV_neon_stats.csv

>>>>

#  `r appendix_NEON_methods_title`

@@

#  `r appendix_tealeaves_methods_title`

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
NEON_table <- read.csv("NEON_height_profiles/NEON_sites_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
NEON_table <- NEON_table[c(1:6)] #select and order columns for inclusion
ft <- flextable(NEON_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .7)
ft <- width(ft, 2, width = .75)
ft <- width(ft, 3, width = 1.5)
ft <- width(ft, 4, width = .5)
ft <- width(ft, 5, width = 1)
ft <- width(ft, 6, width = 1.5)
ft
```

@@

See [here](https://github.com/EcoClimLab/vertical-thermal-review/commit/3f624a119d72d388c707d21fb20666a2ad31848f#commitcomment-55784918) for rows to include.
